Continuous developmental change can explain discontinuities in word learning

### 2019-02-01 cogsci/cogsci.tex
final version cogsci

Experimental results are shown in Figure 6 (top). We first analyzed the
results using a mixed-effects logistic regression with sound distance,
object distance and age group as fixed effects, and with a maximal
random effects structure (allowing us to take into account the full
nested structure of our data) (Barr, Levy, Scheepers, \& Tily, 2013). We
found main effects for all the fixed effects in the regression. For the
sound distance, we obtained \(\beta =\) 0.44 (\(p\) \textless{} 0.001),
replicating previous findings. For object distance, we found \(\beta =\)
0.5 (\(p\) \textless{} 0.001), and this finding confirms the new
prediction of our model. Finally, for the age group, we obtained
\(\beta =\) 0.43 (\(p\) \textless{} 0.001), showing that performance
improves with age. In addition, we found two-way interactions between
sound distance and age (\(\beta =\) 0.17, \(p\) \textless{}0.05) and
between object distance and age (\(\beta =\) 0.18, \(p\)
\textless{}0.05).

We next fit our model (using Equation 2) to the participants' responses
in each age group. The values of \(\Delta s\) and \(\Delta o\) were set
based on data from the similarity judgment task (Figure \ref{fig:stim}).
Thus, the model has two degrees of freedom for each group, i.e.,
\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:data_all} (bottom) shows
the predictions. The model captures the qualitative patterns in both age
groups: starting from a low accuracy recognition when both the sound and
object distances are small, the model correctly predicts an increase in
accuracy when either the sound distance or the object distance
increases. Further, accuracy is correctly predicted to be maximal when
both the sound and object distances are high.

>>>>

Experimental results are shown in Figure 6 (solid lines). We first
analyzed the results using a mixed-effects logistic regression with
sound distance, object distance and age group as fixed effects, and with
a maximal random effects structure (allowing us to take into account the
full nested structure of our data) (Barr, Levy, Scheepers, \& Tily,
2013). We found main effects for all the fixed effects in the
regression. For the sound distance, we obtained \(\beta =\) 0.44 (\(p\)
\textless{} 0.001), replicating previous findings. For object distance,
we found \(\beta =\) 0.5 (\(p\) \textless{} 0.001), and this finding
confirms the new prediction of our model. Finally, for the age group, we
obtained \(\beta =\) 0.43 (\(p\) \textless{} 0.001), showing that
performance improves with age. In addition, we found two-way
interactions between sound distance and age (\(\beta =\) 0.17, \(p\)
\textless{}0.05) and between object distance and age (\(\beta =\) 0.18,
\(p\) \textless{}0.05).

We next fit our model (using Equation 2) to the participants' responses
in each age group. The values of \(\Delta s\) and \(\Delta o\) were set
based on data from the similarity judgment task (Figure \ref{fig:stim}).
Thus, the model has two degrees of freedom for each group, i.e.,
\(\sigma_C\) and \(\sigma_L\). Figure \ref{fig:data_all} (dashed lines)
shows the predictions. The model captures the qualitative patterns in
both age groups: starting from a low accuracy recognition when both the
sound and object distances are small, the model correctly predicts an
increase in accuracy when either the sound distance or the object
distance increases. Further, accuracy is correctly predicted to be
maximal when both the sound and object distances are high.
